\documentclass{letter}
\usepackage[left=1in,top=0.15in,twoside=false]{geometry}
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.7}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

% \signature{Agrim Gupta}
\address{From \\
Mohit Madan\\
Department of Electrical  Engineering\\
Indian Institute of Technology Bombay, Mumbai\\
India\\
E-mail: mohitmadan71@gmail.com
\date{\today}
}

\begin{document}
\begin{letter}{To\\
Prof. Wei Zhang\\
Editor-in-Chief\\
IEEE Wireless Communication Letters}
\vspace{0.5in}


\opening{Dear Prof. Wei Zhang,}

Subject: \textbf{Submission of updated manuscript titled ``Scalar Feedback based Joint Time-Frequency Precoder
  interpolation for  MIMO-OFDM Systems'' for potential publication in
  IEEE Wireless Communication Letters (old reference number  WCL2020-0511).}

Thank you for arranging the prompt reviews of our original manuscript
titled ``Scalar Feedback based Joint Time-Frequency Precoder
interpolation for MIMO-OFDM Systems'' (WCL2020-0511) submitted to the
IEEE Wireless Communications Letters, and providing us an opportunity
to resubmit this manuscript with modifications addressing the issues
raised during the reviews. I would like to thank the reviewers for a
careful reading of the manuscript, as well as for the insightful
points that they have raised regarding various technical aspects of
the manuscript. Based on these reviews, we have madeadditions and
revisions to our submission to address the reviewers concerns. In
particular, we have clarified on the issue of improving past precoder
estimate, as mentioned by Reviwer 2. Please find attached our comments
and actions taken based on the reviews, along with a document
indicative of all the changes made.

The co-authors of this manuscript are
\begin{enumerate}
\item  Agrim Gupta

Department of Electrical  Engineering

Indian Institute of Technology Bombay, Mumbai

India

E-mail: agrim9gupta@gmail.com


\item Prof. Kumar Appaiah

Department of Electrical  Engineering

Indian Institute of Technology Bombay, Mumbai

India

E-mail: akumar@ee.iitb.ac.in

\end{enumerate}

Should you require additional details, please do e-mail me.

Thank you.
\vspace{0.3in}

Sincerely,

Mohit Madan

\end{letter}
\end{document}
